\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english, french]{babel} %français
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{makeidx}
\usepackage{graphicx}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{mathtools} %dcases
\usepackage{braket} %quantum mechanics
\usepackage[colorlinks=true, linkcolor=black, citecolor=black]{hyperref} % hyperlinks
\usepackage{tikz} % drawing in LaTeX
\usepackage{ dsfont } % hollow letters
% the equal sign I use to define something
\newcommand{\define}{\ensuremath{ \overset{\text{def}}{=} }}

\usepackage[%
  figurewithin=section,
  tablewithin=section
]{caption}
\numberwithin{equation}{section}

% differential element
\renewcommand{\d}[1]{\mathrm{d}#1}

% similar symbol with a limit underneath
\newcommand{\simlim}[2]{\ensuremath{ \underset{#1 \rightarrow #2}{\sim} }}

\newcommand{\om}{\ensuremath{\omega}}
\newcommand{\lb}{\ensuremath{\lambda}}
\newcommand{\lbbar}{\ensuremath{\overline{\lambda}}}
\newcommand{\nth}{$n^\text{th}$}

\title{\textbf{Generalities on the Fibonacci Hamiltonian.}}
\author{Nicolas Macé}
\date{9 décembre 2014}
\begin{document}

\selectlanguage{english}

\maketitle

\section{Constructing the Fibonacci Hamiltonian: the alphabet of couplings.}

\subsection{The Fibonacci sequence and its statistical properties}

We consider the following inflation rule on the 2 letters alphabet $\mathcal{A} = \{t_s, t_w \}$:
\begin{equation}
	r \define \begin{cases}
        t_{w} & \rightarrow t_w t_s \\
        t_s & \rightarrow t_w
      \end{cases}
\end{equation} 
Starting from the seed $t_s$, we define the $n^\text{th}$ \emph{Fibonacci word} (aka \emph{rabbit word}):
\begin{equation}
	S_n \define r^{n}(t_s)
\end{equation}
One can show the $S_n$ converges\footnote{For the product topology on $\mathcal{A}^\mathds{N}$ induced by the discrete topology on $\mathcal{A}$.}. We call $S_\infty = \lim_{n \rightarrow \infty} S_n$ the \emph{Fibonacci sequence}.

\textbf{Statistical properties of the Fibonacci sequence}


The inflation rule $r$ has the substitution matrix
\begin{equation}
	\text{Sub}(r) = 
	\begin{bmatrix}
	0 & 1\\
	1 & 1\\
\end{bmatrix}
\end{equation}
The eigenvalues of the substitution matrix are $\tau$ and $\omega \define -1/\tau$, where $\tau = (1+\sqrt{5})/2$ is the golden ratio.
More precisely, we have 
\begin{equation}
	\text{Sub}(r) = \mathcal{R}(\theta) 
	\begin{bmatrix}
	\tau & 0\\
	0 & \omega \\
	\end{bmatrix}
	\mathcal{R}(\theta)^{-1}
\end{equation}
where $\mathcal{R}(\theta)$ is the rotation by the angle $\theta$ such that
\begin{equation}
\begin{cases}
\cos \theta = 1/\sqrt{2+\tau} \\
\sin \theta = 1/\sqrt{2+\omega}
\end{cases}
\end{equation}
Knowing this we can easily compute $\text{Sub}(r^n) = \text{Sub}(r)^n$. We immediately deduce the frequency of letters in $S_n$:
\begin{equation}
	\begin{cases}
	\#\{ t_s \in S_n \}  & = F_{n-2} \\
	\#\{ t_w \in S_n \} & = F_{n-1}
	\end{cases}
\end{equation}
where $F_n$ is the $n^\text{th}$ \emph{Fibonacci number} ($F_0 = 1$, $F_1 = 1$, $F_2 = 2$, ...).
In particular, there are $\tau$ times more $t_w$ than $t_s$ in $S_\infty$.

\subsection{Deflation rules; atoms and molecules.}

Consider the slightly different inflation rule
\begin{equation}
	\tilde{r} = \begin{cases}
        t_{w} & \rightarrow t_s t_w \\
        t_s & \rightarrow t_w
      \end{cases}
\end{equation} 
It has the same substitution matrix as $r$, and therefore the words produced by this rule have the same frequency of letters as the Fibonacci words. Furthermore they are locally undistinguishable from the Fibonacci words\footnote{Both word sequences admit the same 3 local environments: $t_w t_s$, $t_s t_w$ and $t_w t_w$.}. 
Any combination of these two substitution rules (eg $r \tilde{r} r r \tilde{r}...$) has again the same properties. We will also call words produced by such sequences Fibonacci words. 

\textbf{Molecules} \\

\begin{figure}[htp]
\centering
    	\begin{tikzpicture}[scale=.7]
    		\newcommand{\orig}{-1.5}
    		\newcommand{\trans}{1.5}
    		\newcommand{\vertspac}{-2.}
    	
    		% initial chain
    	
    		% bonds 
        	\draw[-] (\orig, 0)  node [left] {$F_{n} (8)$}  -- (\orig+\trans, 0);
			\draw[-,double] (\orig+\trans,0) -- (\orig+2*\trans,0); % node [midway, above] {$t_s$};
			\draw[-] (\orig+2*\trans,0) -- (\orig+3*\trans,0); % node [midway, above] {$t_w$};	
			\draw[-,double] (\orig+3*\trans,0) -- (\orig+4*\trans,0); % node [midway, above] {$t_s$};
			\draw[-] (\orig+4*\trans,0) -- (\orig+5*\trans,0); % node [midway, above] {$t_w$};
			\draw[-] (\orig+5*\trans,0) -- (\orig+6*\trans,0); % node [midway, above] {$t_w$};
			\draw[-,double] (\orig+6*\trans,0) -- (\orig+7*\trans,0); % node [midway, above] {$t_s$};
			\draw[-] (\orig+7*\trans,0) -- (\orig+8*\trans,0); % node [midway, above] {$t_w$};
    	
    		% sites
			\foreach \x in {0,...,7}
		      \filldraw (\orig+\x*\trans,0) circle (0.05); % node [below] {$\ket{\x}$};
		      
			% molecular chains
			
			\foreach \x in {1}
			{
				\draw[-] (\orig, \x*\vertspac) node [left] {$F_{n-2} (3)$} -- (\orig+1.5*\trans, \x*\vertspac);
				\draw[-,double] (\orig+1.5*\trans, \x*\vertspac) -- (\orig+3.5*\trans, \x*\vertspac);
				\draw[-] (\orig+3.5*\trans, \x*\vertspac) -- (\orig+6.5*\trans, \x*\vertspac);
				\draw[-,double] (\orig+6.5*\trans, \x*\vertspac) -- (\orig+8*\trans, \x*\vertspac);
				
				\filldraw (\orig+1.5*\trans,\x*\vertspac) circle (0.05);
				\filldraw (\orig+3.5*\trans,\x*\vertspac) circle (0.05);
				\filldraw (\orig+6.5*\trans,\x*\vertspac) circle (0.05);
			}
		\end{tikzpicture}
\caption{The molecular deflation rule $d_m$ illustrated on a length 8 Fibonacci word.}
\label{fig:mol_defl}
\end{figure}

We have
\begin{equation}
	\tilde{r} r = \begin{cases}
        t_{w} & \rightarrow t_s t_w t_w \\
        t_s & \rightarrow t_s t_w
      \end{cases}
\end{equation} 
Which admits as an inverse the \emph{deflation rule}
\begin{equation}
	d_m = \begin{cases}
        t_{w} & \leftarrow t_s t_w t_w \\
        t_s & \leftarrow t_s t_w
      \end{cases}
\end{equation}
This deflation rule reduces a word of length $F_n$ to word of length $F_{n-2}$ (fig. \eqref{fig:mol_defl}).

\textbf{Atoms} \\

\begin{figure}[htp]
\centering
    	\begin{tikzpicture}[scale=.7]
    		\newcommand{\orig}{-1.5}
    		\newcommand{\trans}{1.5}
    		\newcommand{\vertspac}{-2.}
    	
    		% initial chain
    	
    		% bonds 
        	\draw[-] (\orig, 0)  node [left] {$F_{n} (8)$}  -- (\orig+\trans, 0);
			\draw[-,double] (\orig+\trans,0) -- (\orig+2*\trans,0); % node [midway, above] {$t_s$};
			\draw[-] (\orig+2*\trans,0) -- (\orig+3*\trans,0); % node [midway, above] {$t_w$};	
			\draw[-,double] (\orig+3*\trans,0) -- (\orig+4*\trans,0); % node [midway, above] {$t_s$};
			\draw[-] (\orig+4*\trans,0) -- (\orig+5*\trans,0); % node [midway, above] {$t_w$};
			\draw[-] (\orig+5*\trans,0) -- (\orig+6*\trans,0); % node [midway, above] {$t_w$};
			\draw[-,double] (\orig+6*\trans,0) -- (\orig+7*\trans,0); % node [midway, above] {$t_s$};
			\draw[-] (\orig+7*\trans,0) -- (\orig+8*\trans,0); % node [midway, above] {$t_w$};
    	
    		% sites
			\foreach \x in {0,...,7}
		      \filldraw (\orig+\x*\trans,0) circle (0.05); % node [below] {$\ket{\x}$};
		      
		    % atomic chain
		    
        	\draw[-] (\orig, \vertspac)  node [left] {$F_{n-3} (2)$}  -- (\orig+5*\trans, \vertspac);
			\draw[-,double] (\orig+5*\trans,\vertspac) -- (\orig+8*\trans,\vertspac); % node [midway, above] {$t_s$};
			
			\filldraw (\orig,\vertspac) circle (0.05); % node [below] {$\ket{\x}$};
			\filldraw (\orig+5*\trans,\vertspac) circle (0.05); % node [below] {$\ket{\x}$};
%			\filldraw (\orig+8*\trans,\vertspac) circle (0.05); % node [below] {$\ket{\x}$};
		\end{tikzpicture}
\caption{The atomic deflation rule $d_a$ illustrated on a length 8 Fibonacci word.}
\end{figure}

\subsection{The Fibonacci Hamiltonian and its approximants}

There is a natural quantum system associated to $S_n$. 
It is described by the tight-binding Hamiltonian $H_n$, whose sequence of couplings is given by $S_n$.

\textbf{Boundary conditions:} as there are $F_n$ words in $S_n$, $H_n$ has $F_n$ couplings. These $F_n$ couplings are jump amplitudes between two neighbouring atomic sites. There are thus \textit{a priori} $F_n + 1$ atomic sites, but we are going identify the first and the last atomic sites, ie use \textit{periodic boundary conditions}.
See eq. \eqref{eq:h8} for the example of the sixth Hamiltonian, with $F_6 = 8$ atomis sites.

\begin{equation}
\label{eq:h8} 
	H_6 = 
	\begin{bmatrix}
	0 & t_w &   &   &   &   &   & t_w\\
	t_w & 0 & t_s &   &   &   &   &  \\
	  & t_s & 0 & t_w &   &   &   &  \\
	  &   & t_w & 0 & t_s &   &   &  \\
	  &   &   & t_s & 0 & t_w &   &  \\
	  &   &   &   & t_w & 0 & t_w &  \\
	  &   &   &   &   & t_w & 0 & t_s\\
	t_w &   &   &   &   &   & t_s & 0\\
\end{bmatrix}
\end{equation}

Tha Hamiltonian $H_n$ is called the \textit{$n^\text{th}$ approximant}. $H_\infty = \lim_{n \rightarrow \infty} H_n$ is called the \textit{Fibonacci Hamiltonian}.

\section{Some results on the Fibonacci Hamiltonian}

The transformation $\lambda \rightarrow \lambda H$ leaves the spectrum and the wavefunctions unchanged.
Therefore, the properties of the Fibonacci Hamiltonian relevant for the physics only depend on the parameter
\begin{equation}
	\rho = \frac{t_w}{t_s}
\end{equation}

\subsection{The $\rho = 1$ case.}

In that case the Hamiltonian is periodic. As we are going to see, this case is very special, and differs from the case $\rho < 1$ in almost every respect.

However, we start by analyzing this well known case to gain some insight on the physics of the model.
\\

\textbf{Spectrum of the \nth{} approximant}
It is a tedious but easy exercice of linear algebra to diagonalize the $H_n(k)$ matrix.
One finds that the $F_n$ energy states are indexed by an integer $a \in [0, F_n)$, and write
\begin{equation}
	E_a(k) = 2 \cos \left( \frac{2 a \pi + k}{F_n} \right)
\end{equation}
Then, finding the wavefunction $\ket{\psi_a}$ associated to $E_a$ is easy enought. Calling $\psi(i,a)$ the coefficient of this wavefunction at site $i$, we have the recurrence relation
\begin{equation}
	\psi(i-1,a) + \psi(i+1,a) = E_a \psi(i,a)
\end{equation}
for a site $i$ that is not at the edges of the chain: $i > 0$ and $i < F_n -1$.
Thus $\psi(i,a)$ is a linear combination of $\exp( 2 I \pi i a/F_n )$ and $\exp( -2 I \pi i a/F_n )$. 
If $k = 0, \pi$, the coefficients must be real ($H_n(0,\pi)$ being a \emph{real} symmetric matrix, it can be diagonalized by real vectors), we have, for $i$ integer, $i \in [0, F_n)$,
\begin{equation}
	\psi(i,a) = \mathcal{N}_a \cos \left( \frac{2 a i \pi}{F_n} \right)
\end{equation}
where $\mathcal{N}_a$ is a normalization coefficient. Note that in the limit $n \rightarrow \infty$ it is no longer possible to normalize these extended eigenstates.

I find
\begin{equation}
	\mathcal{N}_a \simlim{n}{\infty} \frac{1}{\sqrt{F_n}} \frac{1}{\sqrt{\frac{1}{2}\left( 1 + \frac{\sin(4 a \pi)}{4 a \pi} \right)}}
\end{equation}

\textbf{Fractal dimensions}
In the case $\rho = 1$ the fractal dimensions of the spectrum can be computed analytically without much effort -- cf. appendix \ref{app:periodic}. 
We find
\begin{align}
	\tau(q \leq 2) &= q-1 \\
	\tau(q \geq 2) &= \frac{q}{2}
\end{align}
In particular, as expected, the Hausdorff dimension is 1. Performing a Legendre transform, we realize that the pointwise Hölder exponent can only take 2 values:
\begin{align}
	\alpha(q \leq 2) &= 1 \text{~and~} f(1) = 1\\
	\alpha(q \geq 2) &= \frac{1}{2} \text{~and~} f(1/2) = 0
\end{align}
$f(1/2) = 0$ indicates that the set of points having Hölder exponent $1/2$ forms at most a countable subset of the spectrum.
It is actually constituted of the 2 points at the edges of the spectral band $[-2,2]$. At these points -- known as Van Hove singularities -- the local density of state is non-smooth (and here even diverges). This is reflected by a smaller than 1 value of the Hölder exponent.

\subsection{The $\rho \rightarrow 1$ limit}

In this limit the Hamiltonian is periodic. Interestingly, physical quantities does not have a smooth limit when $\rho \rightarrow 1$. 
For example if $\rho = 1$ the spectrum is absolutely continuous, but as soon as $\rho < 1$, the spectrum becomes singular continuous. Physically that means that gaps open almost everywhere in the -- previously -- continuous spectral band $[-2,2]$.

The fractal dimensions of the spectrum become smaller than one, indicative of its factal nature.
It was found \cite{Rudinger1996} that, at first order in $(1-\rho)$,
\begin{align}
	q(\tau \leq 1) &= 1+\tau + (1-\rho)4 \pi^{-2} \tau \\
	q(\tau \geq 1) &= 2 \tau
\end{align}
which is easily inverted to deduce that
\begin{equation}
	D(q \leq 2) = 1 - (1-\rho)4 \pi^{-2}
\end{equation}
Note that the $q \geq 2$ dimensions remain unaffected at first order, indicating that the Van Hove singularities are unperturbed.

\subsection{The $\rho \rightarrow 0$ limit}

In this limit, the $t_s$ is much stronger than $t_w$.
As $t_s$ becomes stronger and stronger, the gap width becomes larger and larger. 

To begin with, we investigate the $\rho = 0$ case. 
In that -- rather trival -- case, because $t_w = 0$ the chain decouples into isolated atoms (the ones linked to their neighbours by weak bounds), and isolated molecules (two atoms linked by a strong bound). We will in the following refer to them respectively as ``atoms'' and ``molecules''.

The Hamiltonian is then a direct sum of Hamiltonians decribing an atom or a molecule. Atomic Hamiltonians give rise to a $0$ energy level, while molecular Hamiltonians give rise to two levels: $\pm t_s$.
The spectrum has thus a boring zero Hausdorff dimension. As for the wavefunctions, their fractal dimensions are not even properly defined since the energy levels are degenerate\footnote{The fractal dimension of a linear combination is not the linear combination of the fractal dimensions. But a linear combination of eigenfunctions of a degenerate energy level is again an eigenfunction. Hence the fractal dimensions of the eigenfunctions of a degenerate level are ill-defined.}.

In the $\rho \rightarrow 0$ limit, the atoms and the molecules weakly couple to each other, thus rising the degeneracy of the energy levels. To our delight, the Fibonacci hierarchy of gaps -- indexed according to the gap labelling theorem -- appears.
The Hausdorff dimension of the spectrum satisfyingly becomes non trivial. It is given by
\begin{equation}
\label{eq:haus}
	D(q=0) \simlim{\rho}{0} \frac{\log( \sqrt{2} - 1 )}{\log \rho}
\end{equation}



What about the dimensions of the wavefunctions?
We have
\begin{equation}
\label{eq:wf}
	D(q;a) = x_a \frac{\log 2}{\log \tau}
\end{equation}
where $x_a$ is the fraction of renormalization time the energy labelled by $a$ spends in molecular clusters.

Let us prove it!
Call $\psi_n(i,a)$ the wavefunction associated to the energy $E_a$, at site $i$. Call $I_n(i,a) = |\psi_n(i,a)|^2$ the associated intensity (or presence probability).
We are interested in computing
\begin{equation}
	\chi_n(q;a) = \sum_{i=0}^{F_n - 1} (I_n(i,a))^q
\end{equation}
In the $\rho \rightarrow 0$ limit the intensity at site $i$, at energy $E_a$, only depends on $x_a$. So, given $a$, the intensity does not depend on the site! In other words the intensity is uniform, which means that the fractal dimensions are independant of $q$.

Normalization gives us $I_n(i,a) = 2^{-nx_a}$, so that
\begin{equation}
	\chi_n(q;a) = \left( \frac{1}{2^{n x_a}} \right)^{q-1}
\end{equation}
and
\begin{equation}
	D_n(q;a) = x_a \frac{\log 2}{\log( F_n^{1/n} )}
\end{equation}
hence the result \eqref{eq:wf}.

\newpage
\appendix

\section{The thermodynamical formalism: a reminder.}
\label{app:thermo}

We make an extensive use of the thermodynamical formalism to compute the fractal dimensions of the spectrum and of the wavefunctions. We simply wish here to set up some definitions and recall some useful results.

\subsection{General formalism}

To compute the fractal dimensions of a fractal set $\mathcal{S}$, the thermodynamical formalism defines at each point $a \in \mathcal{S}$ a sequence of open sets $\Delta_a^n \supset \Delta_a^{n+1} \supset ... \supset \{a\}$.
To each of these open sets is associated the propability to draw a point from $\mathcal{S}$ belonging to it. We call it $p_a^n$.
We define the partition function
\begin{equation}
	\Gamma^n(q,\tau) = \sum_a \frac{(p_a^n)^q}{(\Delta_a^n)^\tau}
\end{equation}
Then, one can show \cite{Halsey1986} that the fractal dimensions are given by $\tau(q) = (q-1) D_q$ with $\tau(q)$ defined by
\begin{align}
	\Gamma^n(q,\tau > \tau(q)) &\rightarrow +\infty \\
	\Gamma^n(a,\tau < \tau(q)) &\rightarrow 0
\end{align}

\subsection{Application to the spectrum and to the wavefunctions}
We consider the \nth{} approximant of the infinite chain. 
We will say that is has $L_n$ sites ($L_n = F_n$ in the case of the Fibonacci chain).

In the case of the spectrum, we take $\Delta_a^n$ to be the width of the $a^\text{th}$ energy band. If each energy band has the same degeneracy, we can take $p_a^n = 1/L_n$.

In the case of the wavefunctions, we let $p_i^n = |\psi_i^n|^2$. 

\newpage
\section{Fractal dimensions in the periodic limit.}
\label{app:periodic}

The periodic case is interesting, because the partition function (cf appendix \ref{app:thermo}) can be computed exactly.
We have
\begin{align}
	\Gamma^n &= \left(\frac{1}{L_n}\right)^q\sum_{a=0}^{L_n -1} \frac{1}{(\Delta_a^n)^\tau} \\
	&= 2\left(\frac{1}{L_n}\right)^q\sum_{a=0}^{L_n/2 -1} \frac{1}{(\Delta_a^n)^\tau}
\end{align}
because of the symmetry of the band structure.
Also,
\begin{equation}
	\Delta_a^n \simlim{n}{\infty} \frac{\pi}{L_n} \bigg| \sin \left( \frac{2 a \pi}{L_n} + \frac{\pi}{2 L_n} \right) \bigg|
\end{equation}
We see that in the large $n$ limit, the bandwidths tend to be continuous functions of the band index. We will exploit this fact to transform the sum appearing in the partition function in an integral.
To this end we define $u = 2(a+1/4)/L_n$.
Then, 
\begin{equation}
	\Gamma^n \simlim{n}{\infty} \frac{(L_n)^{\tau + 1}}{(L_n)^q} \frac{1}{\pi^\tau} \underbrace{\int_{1/(2L_n)}^{1 - 3/(2L_n)} \frac{\d{u}}{|\sin(\pi u)|^\tau}}_{ = I_n(\tau)}
\end{equation}
At the edges, the integrand behaves as $1/u^\tau$. Thus if $\tau < 1$, $I_n(\tau)$ converges. We call $I_\infty(\tau)$ its limit.
Thus,
\begin{equation}
	\Gamma^n(\tau <1) \simlim{n}{\infty} \frac{(L_n)^{\tau + 1}}{(L_n)^q} \frac{I_\infty(\tau)}{\pi^\tau}
\end{equation}
We deduce that
\begin{equation}
\boxed{
	q(\tau < 1) = 1+ \tau
	}
\end{equation}
This is the ``trivial'' case, where all the fractal dimensions are equal to 1.

On the other hand, if $\tau > 1$, the integral diverges. We have to evaluate how fast $I_n(\tau)$ diverges. 
The divergencies come from the 2 egdes. At these points, the integrand behaves as $1/u^\tau$, and thus
\begin{equation}
	I_n(\tau > 1) \simlim{n}{\infty} \text{cst}(\tau) \times (L_n)^{\tau -1}
\end{equation}
We conclude that
\begin{equation}
\boxed{
	q(\tau > 1) = 2 \tau
}
\end{equation}

\newpage
\section{Fractal dimensions in the strong quasiperiodicity limit.}
\label{app:qp}
We use again the thermodynamic formalism to compute the fractal dimensions. We introduce the thermodynamic function on the \nth{} approximant:
\begin{equation}
	\Gamma_n(q,\tau; \rho) = \sum_{a=0}^{F_n-1} \frac{(1/F_n)^q}{(\Delta_a^n(\rho))^\tau}
\end{equation}
At first order in $\rho$, atomic and molecular chains are decoupled. Each of the 2 molecular chains involves a fraction $F_{n-2}/F_n$ of the sites, while the atomic chain involves the remaining $F_{n-3}/F_n$ fraction of the sites. So,
\begin{equation}
	\Gamma_n(q,\tau;\rho) = 2 \left( \frac{F_{n-2}}{F_n} \right)^q \Gamma_{n-2}(q, \tau; d_m(\rho)) + \left( \frac{F_{n-3}}{F_n} \right)^q \Gamma_{n-3}(q,\tau; d_a(\rho))
\end{equation}
After a molecular deflation, the coupling $\rho$ is renormalized: $d_m(\rho) = z \rho$ with $z = \rho/2$. Similarly, $d_a(\rho) = \bar z \rho$ with $\bar z = \rho^2$. See \cite{Niu1990}, \cite{Piechon95}.
Because the bandwidths are proportional to the coupling, we obtain,
\begin{equation}
	\Gamma_n(q,\tau;\rho) = 2 \left( \frac{F_{n-2}}{F_n} \right)^q z^{-\tau} \Gamma_{n-2}(q, \tau; \rho) + \left( \frac{F_{n-3}}{F_n} \right)^q \bar{z}^{-\tau} \Gamma_{n-3}(q,\tau; \rho)
\end{equation}
Thus, $\tau(q) = (q-1) D(q)$ is given by
\begin{equation}
\boxed{
	1 = 2 \om^{2q} z^{-(q-1)D(q)} + \om^{3q} \bar{z}^{-(q-1) D(q)}
}
\end{equation}
Now, we look for the Hausdorff dimension, so we take $q=0$. 
We search a $D(0)$ of the form
\begin{equation}
	D(0) = \frac{\log x}{\log \rho}
\end{equation}
then we have an almost-second order equation for $x$:
\begin{equation}
	x^2 = 1 + 2 x 2^{\frac{\log x}{\log \rho}}
\end{equation}
Assuming that $x$ oblidgingly converges to a non-zero constant as $\rho \rightarrow 0$, we have in this limit
\begin{equation}
	x^2 = 1 + 2 x
\end{equation}
hence the result \eqref{eq:haus}.

\newpage
\bibliography{generalities_on_fibo.bib}{}
\bibliographystyle{alpha}
\end{document}